\documentclass[]{template}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "Style Guide"
%
% - 80 character line limit.
% - Start new sentences on a new line.
% - For bulleted paragraphs, put the text in a newline after the \item and keep
%   a consistent two-space indentation.
% - For line wraps anywhere else, make the indentation align with where the text
%   started after the initial tag.
% - Put newlines (double backslash) on their own lines for readability.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{graphicx,xcolor,fontawesome}

\begin{document}

\namesection{Andrew Liu}
{
  \faHome \, \urlstyle{same}\url{https://andrew.cloud/}
  \textcolor{white}{\textbullet} % invisible bullet for spacing
  \faGithub \, \href{https://github.com/MrPickles}{MrPickles}
  \\ % newline for spacing
  \textcolor{white}{\textbullet} % invisible bullet for spacing
  \faEnvelope \, \href{mailto:aliu1@umd.edu}{aliu1@umd.edu}
  \textcolor{white}{\textbullet} % invisible bullet for spacing
  \faLinkedin \, \href{https://linkedin.com/in/liuandrewk}{liuandrewk}
  \textcolor{white}{\textbullet} % invisible bullet for spacing
  \faPhone \, \href{tel:2029059225}{202-905-9225}
}

\section{Education}

\runsubsection{University of Maryland, College Park}
\hfill
\location{Sept 2013 - May 2017 | College Park, MD}
\begin{tightemize}
\item BS in Computer Science, minor in Statistics
\item GPA: 3.97/4.0 --- Magna Cum Laude
\item ACES Cybersecurity Honors Program graduate
\item President's Scholarship recipient
\end{tightemize}

\section{Experience}

\runsubsection{Scale AI}
\descript{Software Engineer}
\hfill
\location{July 2019 – Present | San Francisco, CA}
\begin{tightemize}
\item
  Created a system to apply ML-generated semantic image segmentation predictions
  onto unlabeled images.
  Reduced overall time to produce ground truth semantic segmentation labels on
  images by 30\%.
\item
  Minimized external contractor churn by building a pipeline to proactively
  prepay trusted workers.
  The pipeline determines payment eligibility and infers proper wage
  calculation, sending over \$10,000 per week to workers.
\item
  Founding member of Scale's Machine Learning Infrastructure team.
  Designed and implemented orchestration service to route requests among all ML
  inference microservices via single library call.
  Integrated a frontend on top of the orchestrator to allow non-engineers to
  train models with custom hyperparameter specifications.
\item
  Launched a public-facing dataset curation platform serving millions of images
  from various open source datasets.
\item
  \techstack{
    TypeScript,
    React,
    Python,
    MongoDB,
    PostgreSQL,
    NATS,
    Kubernetes,
    GraphQL
  }
\end{tightemize}

\sectionsep

\runsubsection{Google}
\descript{Software Engineer}
\hfill
\location{August 2017 – July 2019 | Mountain View, CA}
\begin{tightemize}
\item
  Integrated risk-based re-authentication RPC services into various Google
  frontends, scanning over 400 queries-per-second of potential hijacker traffic.
\item
  Maintained various internal authentication API microservices.
  Consulted for projects using these APIs, such as the Secure LDAP G Suite
  service and 2FA in Google Cloud virtual machines.
\item
  Added UI support to Google login for sending Google Prompts to the iOS Gmail
  app.
  Tripled Google Prompt coverage for iOS users to 140 million users.
\item
  Conducted A/B tests and authored Jupyter Notebooks that analyzed data on
  various authentication features.
  Improved pass rate of Google Prompts by 10\% and overall success rate for
  sign-in by 5\% through the aforementioned experiments.
\item
  Migrated Google Authenticator's build system to Bazel and removed all of the
  app's internal dependencies.
  Released an open source version of the Android app on GitHub.
\item
  \techstack{
    Java,
    C++,
    Python,
    JavaScript,
    Soy,
    Guice,
    Dagger,
    Bazel,
    gRPC,
    Jupyter/Colab
  }
\end{tightemize}

\sectionsep

\runsubsection{Dropbox}
\descript{Software Engineering Intern}
\hfill
\location{May 2016 – Aug 2016 | San Francisco, CA}
\begin{tightemize}
\item
  Investigated performance issues with Dropbox's web server.
  Fixed server inefficiencies, reducing the loading time of Dropbox's website
  homepage by 33\% as a result of various optimizations.
\item
  Implemented an end-to-end promotional flow on the Dropbox website to let users
  request team upgrades to Dropbox Business.
  Integrated with an RPC service to send email campaigns to Dropbox team admins.
\item
  \techstack{
    Python,
    React,
    Pxyl,
    Vagrant
  }
\end{tightemize}

\sectionsep

\runsubsection{Google}
\descript{Software Engineering Intern}
\hfill
\location{May 2015 - Aug 2015 | Kirkland, WA}
\begin{tightemize}
\item
  Created an exploitability detection module in Breakpad (an open source crash
  reporting suite) that predicts whether a program crash occurred due to
  attacker exploitation.
  Implemented triage heuristics such as buffer overflow detection and binary
  permission checking.
\item
  Pushed all internal changes upstream to the open source version of Breakpad.
\end{tightemize}

\sectionsep

\runsubsection{US Army Research Laboratory}
\descript{Security Researcher}
\hfill
\location{May 2014 - Aug 2014 | Adelphi, MD}
\begin{tightemize}
\item
  Coauthored a research paper for the USENIX security conference.
  The paper details the usage of code stylometry and machine learning as a means
  of authorship attribution for anonymous source code samples.
\item
  Wrote a web crawler to scrape historical source code entries from the Google
  Code Jam programming competition.
  Cleaned up scraped source code samples to use as a corpus of training data.
\end{tightemize}

\lastupdated

\end{document}
\documentclass[]{article}
